---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align='center',
  dpi = 300
)
```

# segregatr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/segregatr)](https://CRAN.R-project.org/package=segregatr)
[![](https://cranlogs.r-pkg.org/badges/grand-total/segregatr?color=yellow)](https://cran.r-project.org/package=segregatr)
[![](https://cranlogs.r-pkg.org/badges/last-month/segregatr?color=yellow)](https://cran.r-project.org/package=segregatr)
<!-- badges: end -->

The goal of **segregatr** is to provide segregation analysis for clinical variant classification.

## Installation

You can install **segregatr** from CRAN as follows:
```{r, eval = FALSE}
install.packages("segregatr")
```

Alternatively, obtain the latest development version from GitHub:
```{r, eval = FALSE}
devtools::install_github("magnusdv/segregatr")
```

## Example

```{r, message=F}
library(segregatr)
```

The family below shows four brothers, all affected with a rare dominant disease with 90% penetrance and phenocopy rate 1%. The parents have unknown affection status. All four brothers are shown to carry a candidate variant.

```{r sibex, echo = F, results = F, fig.height = 2.4, fig.width = 3, out.width = "40%"}
x = nuclearPed(4)
plotSegregation(x, affected = 3:6, unknown = 1:2, proband = 3, carriers = 3:6, margins = 1.5)
```

We will use **segregatr** to analyse the co-segregation of the variant and the disease in this pedigree. Specifically we want to compute the *full-likelihood Bayes factor* (FLB), quantifying the evidence that the variant is pathogenic.

To create the pedigree we use the `nuclearPed()` function from the **pedtools** package, which is automatically loaded together with **segregatr**.

```{r}
x = nuclearPed(4)
```

Then we run the `FLB()` function, filling in the necessary data:
```{r}
FLB(x, carriers = 3:6, affected = 3:6, unknown = 1:2,
    freq = 0.0001, penetrances = c(0.01, 0.9, 0.9), proband = 3)
```

The resulting FLB score is less than 8, which unfortunately only indicates suggestive evidence for pathogenicity.
