---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# segregatr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/segregatr)](https://CRAN.R-project.org/package=segregatr)
[![](https://cranlogs.r-pkg.org/badges/grand-total/segregatr?color=yellow)](https://cran.r-project.org/package=segregatr)
[![](https://cranlogs.r-pkg.org/badges/last-month/segregatr?color=yellow)](https://cran.r-project.org/package=segregatr)
<!-- badges: end -->

The goal of **segregatr** is to provide segregation analysis for clinical variant classification.

## Installation

You can install **segregatr** from CRAN as follows:

```{r, eval = FALSE}
install.packages("segregatr")
```

Alternatively, you can obtain the latest development version from GitHub:
```{r, eval = FALSE}
devtools::install_github("magnusdv/segregatr")
```

## Example

We start by loading **segregatr**:
```{r}
library(segregatr)
```

The family below shows four brothers, all affected with a rare dominant disease with 90% penetrance and phenocopy rate 1%. The parents have unknown affection status. All four brothers are shown to carry a candidate variant, warranting a segregation analysis. pathogenic variant.

```{r sibex, echo = F, results = F, fig.height = 2.5, fig.width = 3, fig.align='center', out.width = "35%"}
x = nuclearPed(4)
plotSegregation(x, affected = 3:6, unknown = 1:2L, proband = 3,
                carriers = 3:6, margins = c(1,3,1,1))
```

In order to compute the full-likelihood Bayes factor, we first create the pedigree.

```{r}
x = nuclearPed(4)
```

Then we run the `FLB()` function, filling in the necessary data:
```{r}
FLB(x, carriers = 3:6, aff = 3:6, unknown = 1:2,
    freq = 0.0001, penetrances = c(0.01, 0.9, 0.9), proband = 3)
```

The answer indicates only suggestive evidence for pathogenicity.
