---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# segregatr

<!-- badges: start -->
<!-- badges: end -->

The goal of **segregatr** is to provide segregation analysis for clinical variant classification.

## Installation

You can install the development version of **segregatr** from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("magnusdv/segregatr")
```

```{r}
library(segregatr)
```

## Example

The family below shows four brothers, all affected with a rare dominant disease with 90% penetrance and phenocopy rate 1%. The parents have unknown affection status. All four brothers are shown to carry a candidate variant, warranting a segregation analysis. pathogenic variant.

```{r sibex, echo = F, results = F, fig.height = 2.5, fig.width = 3, out.width = "40%"}
x = nuclearPed(4)
plotSegregation(x, affected = 3:6, unknown = 1:2L, proband = 3,
                carriers = 3:6, margins = c(1,3,1,1))
```

In order to compute the full-likelihood Bayes factor, we first create the pedigree.

```{r}
x = nuclearPed(4)
```

Then we run the `FLB()` function, filling in the necessary data:
```{r}
FLB(x, carriers = 3:6, aff = 3:6, unknown = 1:2,
    freq = 0.0001, penetrances = c(0.01, 0.9, 0.9), proband = 3)
```

The answer indicates only suggestive evidence for pathogenicity.
